Actuator line modeling of vertical-axis turbines

### 2016-04-29 paper.tex
Add acknowledgments

\acks These are the acknowledgments

>>>>

\acks The authors would like to acknowledge funding through a National Science
Foundation CAREER award (principal investigator Martin Wosnik, NSF 1150797,
Energy for Sustainability, program manager Gregory L. Rorrer). This work has
been carried out as part of author P. Bachant's PhD research at the University
of New Hampshire.
